---
title: "EAES 420 Midterm Starter"
author: "Vincent Baker"
date: "3/24/23"
output: html_document
---

## Academic Honesty Statement

*I, Vincent Baker, hereby state that I will not communicate with or gain information in any way from my classmates, or copy work from past assignments, during this exam, and that all work is my own.*

## Load packages

```{r load-packages, message = F}
library(tidyverse)
library(openintro)
```

## Exericses

### Exericse 1

```{r earhtquakes}
glimpse(earthquakes)
```

1) There are 123 rows and 7 variables in the dataset. 

2) Three variables are categorical and the other four are numerical. 

### Exericse 2

```{r earthquakes-names}
names(earthquakes)
```

"area of world" shows specific states, countries, and/or provinces, so maybe it's a general term, and "region" is specifically listing the countries where these earthquakes have been recorded. 

### Exericse 3

```{r regional-observations}
count(earthquakes, region, wt = NULL, sort = TRUE)
```

I could have also used '%>%' and the 'group_by' function to check the number of observations in each region. 

### Exericse 4

[Enter code and/or narrative here.]

### Exericse 5

[Enter code and/or narrative here.]

### Exericse 6

[Enter code and/or narrative here.]

### Exericse 7

```{r visualize-earthquakes-deaths, eval = F}
earthquakes_subset %>% 
  ggplot(aes(x = month, y = deaths)) +
  geom_violin() +
  theme_classic()
```

[Enter code and/or narrative here.]

### Exericse 8

[Enter code and/or narrative here.]
