---
title: "EAES 420 Midterm Starter"
author: "Vincent Baker"
date: "3/24/23"
output: html_document
---

## Academic Honesty Statement

*I, Vincent Baker, hereby state that I will not communicate with or gain information in any way from my classmates, or copy work from past assignments, during this exam, and that all work is my own.*

## Load packages

```{r load-packages, message = F}
library(tidyverse)
library(openintro)
```

## Exericses

### Exericse 1

```{r earhtquakes}
glimpse(earthquakes)
```

1) There are 123 rows and 7 variables in the dataset. 

2) Three variables are categorical and the other four are numerical. 

### Exericse 2

```{r earthquakes-names}
names(earthquakes)
```

"area of world" shows specific states, countries, and/or provinces, so maybe it's a general term, and "region" is specifically listing the countries where these earthquakes have been recorded. 

### Exericse 3

```{r regional-observations}
count(earthquakes, region, wt = NULL, sort = TRUE)
```

I could have also used '%>%' and the 'group_by' function to check the number of observations in each region. 

### Exericse 4

```{r visualize-earthquake-regions, eval = T}
earthquakes %>% 
  filter(region %in% c("Turkey", "Iran", "China", "Japan", "United States")) %>% 
  ggplot(aes(x = region)) +
  geom_bar() +
  theme_classic() +
  theme(axis.text.x = element_text(angle=90, hjust=1))
```

### Exericse 5

```{r visualize-earthquake-richter, eval = T}
earthquakes %>% 
  filter(region %in% c("Turkey", "Iran", "China", "Japan", "United States")) %>% 
      ggplot(aes(x = richter, fill = region)) +
      geom_histogram(binwidth = 0.5) +
      facet_wrap(~region, 
             ncol = 3) +
      theme_classic()
```

The average richter value for all of these regions seems to be ~7-7.5. I don't think this average depends on the region because all of the histograms show that the majority of earthquakes in each region are about 7.5 magnitude. 

### Exericse 6

```{r earthquakes-subset}
earthquakes_subset <- earthquakes %>%
  select(richter, year, month, deaths) %>%
  filter(!is.na(deaths))
earthquakes_subset
```

Two rows have been removed from this new dataset. 

### Exericse 7

```{r visualize-earthquakes-deaths, eval = F}
earthquakes_subset %>% 
  ggplot(aes(x = month, y = deaths)) +
  geom_violin() +
  theme_classic()
```

[Enter code and/or narrative here.]

### Exericse 8

[Enter code and/or narrative here.]
